\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Add colon before a list
Split CID and Authority Key. If the ID includes authentication information, it's impossible to revoke keys without completely republishing the content - graceful migration should be possible (how exactly to do it is another question).

The platform maintains state about the available data, and how it is distributed, in the \textit{data directory}. All data objects stored correspond to one among a finite set of \textit{data object types}. Each type is meant to capture the following storage and distribution requirements for some broader family of objects

@@

\begin{itemize}
  \item[-] \textbf{ID:} Unique integer identifier.
  \item[-] \textbf{Description:} Human readable description.
  \item[-] \textbf{Size Limit:}When set, represents the maximum number of bytes.
  \item[-] \textbf{Replication Factor:} Number of storage providers which should replicate objects of this type.
  \item[-] \textbf{Storage Tranches:} Set of tranche IDs which can be used with this data type. If empty, then any tranche may be used.
  \item[-] \textbf{Active:} Whether objects of this type can be added at this time.
\end{itemize}
\end{concept_box}

@@

  \item[-] \textbf{CID:} A content identifier which allows for secure authentication of the data under some implicit chunking schema.

>>>>

The platform maintains state about the available data, and how it is distributed, in the \textit{data directory}. All data objects stored correspond to one among a finite set of \textit{data object types}. Each type is meant to capture the following storage and distribution requirements for some broader family of objects:

@@

\begin{itemize}
  \item[-] \textbf{ID:} Unique integer identifier.
  \item[-] \textbf{Description:} Human readable description.
  \item[-] \textbf{Size Limit:} When set, represents the maximum number of bytes.
  \item[-] \textbf{Replication Factor:} Number of copies for data objects of this type that must exist in the storage system at any time. The simplest interpretation for this is the minimum number of storage providers that must replicate the data object.
  \item[-] \textbf{Storage Tranches:} Set of tranche IDs which can be used with this data type. If empty, then any tranche may be used.
  \item[-] \textbf{Active:} Whether objects of this type can be added at this time.
\end{itemize}
\end{concept_box}

@@

  \item[-] \textbf{CID:} A content identifier.

  \item[-] \textbf{Authority Key:} A public key (hash) which allows for secure authentication of the data (under some implicit chunking schema).
